Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-24 paper-v1.tex
fix description fig 1 by @naszam
English fixes via Google autocorrection

Peer-review is a necessary and essential quality control step for scientific publications but lacks proper  incentives. Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected in the timeliness, quality and fairness. Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation. We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum. If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their assessed quality. To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.

@@

Peer review is still the only quality control mechanism devoted to evaluate scientific outcomes. The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}. However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.

@@

\subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision \cite{Tennant2017-F1000R}, such as gender or cultural discrimination and social prestige of the institution. To solve this problem some journals have implemented \emph{double-blind review} process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.

@@

\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.

@@

\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on blockchain networks.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).

@@

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}. \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions. ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}. \textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.

@@

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might set a first step in this standardization. We hope that soon the value of peer review as public good will be recognized by research funders and hiring committees.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}

>>>>

Peer-review is a necessary and essential quality control step for scientific publications but lacks proper  incentives. Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected in timeliness, quality and fairness. Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation. We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum. If requirements are met, peer-reviews will be accepted and paid by the approver proportionally to their assessed quality. To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.

@@

Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes. The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}. However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.

@@

\subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision \cite{Tennant2017-F1000R}, such as gender or cultural discrimination and social prestige of the institution. To solve this problem some journals have implemented \emph{double-blind review} process (the identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.

@@

\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.

@@

\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, units of values registered on blockchain networks.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible. This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).

@@

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\small{
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
\label{fig:contracts}
\end{figure}

@@

\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}. \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions. ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents. Future developments will allow leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}. \textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview. It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as a template to build an AZTEC-compatible asset.

@@

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might set a first step in this standardization. We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Simona Pop, Evan C. Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
